\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Carlos}{Hernandez}{Software Engineer}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
	Guatemala City
	(502) 4276 6154
	~
	\href{mailto:learnercys@gmail.com}{learnercys@gmail.com}
	% TODO when this is available, use it instead of linkedin and github
	%      and maybe the email(think about it)
	% \href{https://learnercys.github.io/}{learnercys.github.io}	
	\href{https://www.linkedin.com/in/carlos-hernandez-1571b187}{linkedin}
	\href{https://github.com/learnercys}{github}
\section{Language}
	Spanish
	English
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\begin{entrylist}
\entry
	{2015-present}
	{Paypal}
	{Guatemala city}
	{
		\emph{Software Engineer} \\
		Paypal is a company operating a worldwide online payments system that supports online money transfers
		and serves as an electronic alternative to traditional paper methods. As a Software Engineer working for
		Paypal I develop projects based in RESTful services using NodeJS as main technology that are required to:

		\begin{itemize}
			\item Handle accounts and pay bills from the U.S. to multiples countries.
			\item Allow users to send money to multiples countries.
		\end{itemize}
	}

\entry
	{2014-2015}
	{Kipo Business}
	{Guatemala city}
	{
		\emph{Frontend Developer} \\
		Kipo Business is a platform designed to manage and monitor activities in real time for your employees that
		work out of the office. As a Frontend Developer I manage and schedule the development tasks, create the 
		architecture and define the technologies to be used.

		\begin{itemize}
			\item Develop solutions for real time geolocation using Google Maps and AngularJS.
			\item Build solutions to Data-Driven Documents based on D3js and Google Charts Library.
			\item Integration with APIs based on RESTful Services.
		\end{itemize}
	}
	
\entry
	{2013--2014}
	{Claro}
	{Guatemala city}
	{
		\emph{System Analyst} \\
		Claro is a mobile telecommunications services provider, domestic and international
		long distance telephone, data transmission and pay television services. Working for Claro I develop and support 
		the Mobile Area projects, my main functions were:

		\begin{itemize}
			\item Develop frontend and backend applications.
			\item Managing of new requirements and support to the current systems.
			\item System and Database Administration.
			\item Processes optimization.
		\end{itemize}
	}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

% TODO: uncomment this :)
% \entry
% 	{2018--present}
% 	{Applied Mathematics}
%	{Universidad del Valle de Guatemala.}
%	{}
\entry
	{2011--2016}
	{Science and System Engineering}
	{Universidad de San Carlos de Guatemala.}
	{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	VOLUNTER SECTION
%----------------------------------------------------------------------------------------
\section{Volunter}
\begin{entrylist}
\entry
	{2017-present}
	{NodeSchool}
	{Guatemala City}
	{
		\href{https://nodeschool.io}{NodeSchool} is a worldwide open source project run by volunters with two goals: Create high quality
		programming and to host community learning events. As a \href{https://nodeschool.io/guatemala/}{NodeSchool Mentor}
		I help from begginers to experts to learn about web technologies.
	}
\end{entrylist}

% TODO delete this as possible, ugh!
\clearpage
%----------------------------------------------------------------------------------------
%   PROGRAMMING SECTION
%----------------------------------------------------------------------------------------
\section{Skills}

\textbf{Frontend}

\begin{itemize}
	\item HTML and Template Engines.
	\item CSS, CSS Preprocessors, Bootstrap, Bootstrap Grid System, Boostrap UI, Material Design and Media Queries.
	\item JavaScript, Prototype, DOM Manipulation, jQuery, CoffeeScript, AngularJS, React.
	\item Google Tools and APIs: Google maps, Analytics, Google Charts.
	\item Grunt and Gulp.
\end{itemize}

\textbf{Backend}
\begin{itemize}
	\item NodeJS with Express, Restify and Hapi.
	\item SocketIO.
	\item Python and Django.
	\item RESTful Services.
\end{itemize}

\textbf{Databases}
\begin{itemize}
	\item MySQL.
	\item Microsoft SQL Server.
	\item PL/SQL.
\end{itemize}

\textbf{General}
\begin{itemize}
	\item Version Control - Git, Git Flow, Github Flow.
	\item Operation Systems: Linux, Windows and iOS.
\end{itemize}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{Professional:} Software Architecture, Artificial Intelligence, Software Security. Fan to the new technologies and software development designs.

\textbf{Personal:} Internet, Chess, Mathematics, Physics, Entomology.

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------
\section{References}

\begin{itemize}
	\item \noindent \textbf{Axel Mayorga Ruballos},  Software Architect at Kipo Inc. \hfill \hfill (502) 4216-9351
	\item \noindent \textbf{Kevin Eduardo López}, Software Engineer at Viscosity North America\hfill \hfill (502) 3036-2000
\end{itemize}
\end{document}
